\section{Applications}
\label{subsec:applications}
One of the main intended applications is in agriculture. As the bee population is dwindling, such MAV(Micro-aerial vehicle) swarms can prove a suitable replacement and help with sustainability. Moreover, closed-space hydroponics and aeroponics systems currently rely on manual pollination---a task that can be automated with MAV swarms. 
\par Some plant species need to be pollinated in bursts due to their short bloom period. Currently, this is achieved by moving bee hives to the desired location, but this could also be achieved with a robotic swarm. All this shows the substantial improvements to agriculture that such a system could bring.
\par Artificial swarms can also be incredibly useful in search-and-rescue scenarios. Having a fault-tolerant system that quickly covers a wide area, even in difficult conditions, could be the difference between life and death.   
\par A robotic swarm could be used to sweep a battlefield and discover mines and bombs, greatly reducing the risk for teams that dispose of unexploded ordnance.
\par Identifying radiation, chemical, and biological hazards is another dangerous task that could be effectively performed by artificial swarms. If employed, such a system could protect the health and lives of professionals in the field. 
\par Another possible application is security. A swarm of unpredictably moving tiny robots eliminates blind spots of stationary cameras. This can in turn greatly aid law enforcement and justice. 
\par Exploration of hard-to-reach areas is another task well-suited to artificial swarms, particularly in connection with space exploration and eventual colonization.
\par Yet another possiblity is environmental monitoring such as tracking and reducing water pollution.
\par Moreover, it could be used to find and track endangered species, helping with their preservation. Finally, lost farm animals can also be located with such a system. 
\par The simulation in particular could help determine optimal parameters for the system when used in practice.  

